Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-01-20 analysis/TAS_memo/memo_TAS_reviewers.Rmd
minor edits

[INSERT]

@@

Suppose prosecutors from the same office were all exposed to training on how best to strike Black jurors. If so, our approach allows for (but does not require) aggregating all those prosecutors' cases, i.e., acting as if all prosecutors from that office were a single individual prosecutor (e.g., the strike bias of the "DA's office"). Once aggregated, any down-weighting adjustment (choosing $\alpha < 1$) depends on assumptions about how dissimiliarities between the trial-level characteristics (e.g., defendant race, offense type) in the current trial and in past trials may still produce incompatibilty, notwithstanding the prosecutors' common exposure to the training. If none, one could assign equal weight to the historical data ($\alpha$ = 1). If one allows for some incompatibilty nonetheless, one could either subset the historical data (sacrificing power) to include only those past trials that share the same trial-characteristics as the bias-salient characteristics of current trial. Or one could keep all the historical trials; choose an $\alpha$ value to match the degree of suspected incompatibility; and check for how sensitive any bias detection is values of alpha.

>>>>

[We see expository burden but . . .. ]

@@

Suppose prosecutors from the same office were all exposed to training on how best to strike Black jurors. If so, our approach allows for (but does not require) aggregating all those prosecutors' cases, i.e., acting as if all prosecutors from that office were a single individual prosecutor (e.g., the strike bias of the "DA's office"). Once aggregated, any down-weighting adjustment (choosing $\alpha < 1$) depends on assumptions about how dissimiliarities between the trial-level characteristics (e.g., defendant race, offense type) in the current trial and in past trials may still produce incompatibilty, notwithstanding the prosecutors' common exposure to the training. If none, one could assign equal weight to the historical data ($\alpha$ = 1). If one allows for some incompatibilty nonetheless, one could either subset the historical data (sacrificing power) to include only those past trials that share the same trial-characteristics as the bias-salient characteristics of current trial. Or one could keep all the historical trials; choose an $\alpha$ value to match the degree of suspected incompatibility; and check for how sensitive any bias detection is to values of alpha.
